Sexual selection improves population fitness: a meta-analysis

### 2018-06-21 meta_analysis_sexual_selection_pop_fitness.Rmd
21/6 Update 2

### Effect Size Calculation

A spreadsheet describing the data that was extracted from each of the included studies is included as supplementary material. It details the type of data collected for each study (arithmatic means, SD, n, F-statistic, chi-squared, proportion etc.). The rules utilised were as follows:

>>>>

### Data Extraction and Effect Size Calculation

The rules utilised during the data extraction and effect size calculation were as follows:
